### 2022-08-15 introduction.tex
Reorder introduction content

% despite available aligners, there is room for improvement
% summarize sentence into ~ "alignment is performed in the amino acid space"
A common strategy is to perform alignment inference in the amino acid space
\parencite{bininda2005transalign,abascal2010translatorx}.
While this approach is an improvement over DNA models, it discards information,
underperforms compared to alignment at the codon level, and fails in the
presence of artifacts such as frameshifts and early stop codons.
% to correct this common practice is to discard lots of data
Given that errors and artifacts are common in molecular data, this requires
costly curation practices that discard large amounts of information.
% errors in genomic data that lead to erroneous downstream analyses
Errors in genomic datasets can lead to erroneous results in
functional and comparative genomic studies \parencite{estimates_schneider_2009}.

% to address this, we present COATi
Here we present COATi, short for COdon-Aware Alignment Transducer, a statistical
pairwise aligner that incorporates codon substitution models and is
robust to artifacts present in genomic data.

>>>>

% despite available aligners, there is room for improvement
% summarize sentence into ~ "alignment is performed in the amino acid space"
A common strategy is to perform alignment inference in the amino acid space
\parencite{bininda2005transalign,abascal2010translatorx}.
While this approach is an improvement over DNA models, it discards information,
underperforms compared to alignment at the codon level, and fails in the
presence of artifacts such as frameshifts and early stop codons.
% errors in genomic data that lead to erroneous downstream analyses
Errors in genomic datasets can lead to erroneous results in
functional and comparative genomic studies \parencite{estimates_schneider_2009}.
% to correct this common practice is to discard lots of data
Given that errors and artifacts are common in molecular data, this requires
costly curation practices that discard large amounts of information.
% to address this, we present COATi
To address this, we present COATi, short for COdon-Aware Alignment Transducer,
a statistical pairwise aligner that incorporates codon substitution models and
is robust to artifacts present in genomic data.
